---
title: "Subemble"
author: "Yehu Chen"
date: "2018/1/29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(nnls)
library(SuperLearner)

# Review available models.
listWrappers()
```

```{r}
filename = "Binomial_dataset_5_final.txt"
data = read.csv(filename)

data_train = data[c(1:225),]
data_test = data[c(226:300),]

#X_train = data_train[,c(2:100)]
#X_test = data_test[,c(2:100)]
#Y_train = data_train[,c(1)]
#Y_test = data_test[,c(1)]

X_train = data_train[,c(2:ncol(data_train))]
Y_train = data_train[,c(1)]
X_test = data_test[,c(2:ncol(data_test))]
Y_test = data_test[,c(1)]

sample_data_vector = c()

# number of subsemble
N = 1000

# size of subsemble
n = 50

for(i in 1:N){
  sample_data_vector = c(sample_data_vector,sample(ncol(X_train),n))
}

```

SL.svm.4 = function(..., family = "binomial", kernel = "polynomial", degree = 4, coef0 = 1) {
  SL.svm(..., family = family, kernel = kernel, degree = degree, coef0 = coef0)
}


SL.svm.6 = function(...,family = "binomial",kernel = "sigmoid",coef0 = 0) {
  SL.svm(...,family = family, kernel = kernel,coef0 = coef0)
}

SL.svm.11 = function(..., kernel = "radial", coef0 = 1,family = binomial()) {
  SL.svm(...,kernel = kernel, coef0 = coef0,family = family)
}

SL.glmnet.0.50 <- function(..., alpha = 0.50,family="binomial"){
  SL.glmnet(..., alpha = alpha, family = family)
}

```{r}
library(caret)
library(lattice)
library(ggplot2)

SL.svm.1 = function(..., kernel = "linear") {
  SL.svm(..., kernel = kernel)
}

SL.svm.2 = function(..., kernel = "polynomial", degree = 2, coef0 = 1) {
  SL.svm(..., kernel = kernel, degree = degree, coef0 = coef0)
}

SL.svm.3 = function(..., kernel = "polynomial", degree = 2, coef0 = 10) {
  SL.svm(..., kernel = kernel, degree = degree, coef0 = coef0)
}

SL.svm.4 = function(..., kernel = "polynomial", degree = 4, coef0 = 1) {
  SL.svm(..., kernel = kernel, degree = degree, coef0 = coef0)
}

SL.svm.5 = function(..., kernel = "polynomial", degree = 4, coef0 = 10) {
  SL.svm(..., kernel = kernel, degree = degree, coef0 = coef0)
}

SL.svm.6 = function(..., kernel = "sigmoid",coef0 = 0) {
  SL.svm(..., kernel = kernel,coef0 = coef0)
}

SL.svm.7 = function(..., kernel = "sigmoid",coef0 = 1) {
  SL.svm(..., kernel = kernel,coef0 = coef0)
}

SL.svm.10 = function(...,type.class = "C-classification", cost = 3) {
  SL.svm(...,type.class = type.class, cost = cost )
}

SL.svm.11 = function(..., kernel = "radial", coef0 = 1) {
  SL.svm(..., kernel = kernel, coef0 = coef0)
}

SL.svm.12 = function(..., kernel = "radial", coef0 = 10) {
  SL.svm(..., kernel = kernel, coef0 = coef0)
}
SL.glmnet.0 <- function(..., alpha = 0,family="binomial"){
  SL.glmnet(..., alpha = alpha , family = family)
}

SL.glmnet.1 <- function(..., alpha = 1,family="binomial"){
  SL.glmnet(..., alpha = alpha , family = family)
}

SL.glmnet.0.25 <- function(..., alpha = 0.25,family="binomial"){
  SL.glmnet(..., alpha = alpha, family = family)
}

SL.glmnet.0.50 <- function(..., alpha = 0.50,family="binomial"){
  SL.glmnet(..., alpha = alpha, family = family)
}

SL.glmnet.0.75 <- function(..., alpha = 0.75,family="binomial"){
  SL.glmnet(..., alpha = alpha, family = family)
}

#"SL.svm.1","SL.svm.2","SL.svm.3",
#"SL.svm.5","SL.svm.6","SL.svm.12",
#"SL.svm.7","SL.glmnet","SL.svm.10","SL.svm.11",
my_library = c("SL.svm.4",
               "SL.glmnet",
               "SL.nnls")
```


# run sl for all subemble
```{r}
predictions = c()
for(i in 1:N){
  X_index = sample_data_vector[(n*i-n+1):(n*i)]
  sl = SuperLearner(Y=Y_train, X = X_train[,c(X_index)], family=binomial(),SL.library=my_library)
  pred = predict(sl, X_test[,c(X_index)], onlySL = T)
  risk = 0
  for(j in 1:75){
    if( (pred$pred[j]>=0.8) && (Y_test[j]==1) ){
      risk = risk + 1
    }
    if( (pred$pred[j]<0.5) && (Y_test[j]==0) ){
      risk = risk + 1
    }
  }
  predictions = c(predictions,risk)
}

```

# rank the predictions and select the top 10% indexes
```{r}
threshold = sort(predictions, decreasing = TRUE)[as.numeric(N/10)]
top_index = c()
for(i in 1:length(predictions)){
  if(predictions[i]>=threshold){
    top_index = c(top_index,i)
  }
}
```

# use prediction top index to get index of data features
```{r}
feature_index = c()
for(i in 1:length(top_index)){
  for(j in 1:n){
    feature_index = c(feature_index,sample_data_vector[(n*i+j)])
  }
}
```

# barplot the feature frequency
```{r}
barplot(table(feature_index))
sort(table(feature_index), decreasing=TRUE)[1:20]
```

